The Astropy Project

### 2017-10-26 main.tex
quotes
latex macro

\cite{Lupton2004} describe an “optimal” algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays. The \package{visualization} package provides a convenience function to create such a color image.  It also includes an associated set of classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.

@@

The documentation for many Python packages the core \package{astropy} package as well as for all packages in the Astropy ecosystem is written using the Sphinx package. This package makes it possible to write the documentation using plain text files that follow a markup language called reStructuredText, and Sphinx can then transform this into HTML or \LaTeX documentation. As part of the project, we have developed a few extensions that facilitate generating documentation for a large project like Astropy. One of the main extensions we have developed is \package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}}, which makes it easy with a single reStructuredText command to generate a set of documentation pages listing all the available classes, functions, and attributes in any given Python module.

>>>>

\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays. The \package{visualization} package provides a convenience function to create such a color image.  It also includes an associated set of classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.

@@

The documentation for many Python packages the core \package{astropy} package
as well as for all packages in the Astropy ecosystem is written using the
Sphinx package. This package makes it possible to write the documentation using
plain text files that follow a markup language called reStructuredText, and
Sphinx can then transform this into HTML or \LaTeX{} documentation. As part of
the project, we have developed a few extensions that facilitate generating
documentation for a large project like Astropy. One of the main extensions we
have developed is
\package{sphinx-automodapi}\footnote{\url{http://sphinx-automodapi.readthedocs.io}},
which makes it easy with a single reStructuredText command to generate a set of
documentation pages listing all the available classes, functions, and
attributes in any given Python module.
